\section{Project Objectives} \label{project-objectives}

\subsection{Use of minigames in interactive learning}

Create some minigames to make learning more interactive and more intriguing for students.

\subsection{Use AI to help develop a more compelling learning experience}

Use AI to generate compelling descriptions of the topics, to make learning funnier.

\subsection{Make learning science more approachable and enjoyable}

Make the platform an accessible starting point in the learning of science, to allow everyone to learn science using intuition and reason.

\subsection{Provide single-topic focused content}

Providing single topic courses means the possibility to create a learning path specific for the interests of the user.

\subsection{Provide private classes as instances of a course}

Create classes, from the general courses, to allow teachers/professors to integrate the platform in their standard lectures.

\subsection{Allow better student-professor interaction}

Using the classes the professors can understand which topics are clearer and then provide feedback. Moreover students can easily determine the level of comprehension of each topic before a test.

\subsection{Provide quality guarantees on the material published}

Have personnel checking the validity of the published material, while not interfering with the private resources.

\subsection{Collect data and provide a progress history}

For the learning user, having feedback on the level of comprehension is fundamental and will help them focus more on the less understood topics.